### 2022-05-18 Publish Paper/manuscript_main.tex
Update Publish Paper

		MobileNetV3Large-Layer[:270] + Soft-Attention & 0.71 \\

@@

		MobileNetV3Large-Layer[:266] + Soft-Attention & 0.73 \\

@@

		MobileNetV3Large-Layer[:260] + Soft-Attention & 0.77 \\

@@

		MobileNetV3Large-Layer[:251] + Soft-Attention & 0.79 \\

@@

		MobileNetV3Large-Layer[:246] + Soft-Attention & 0.84 \\

@@

		MobileNetV3Large-Layer[:246] + Soft-Attention + Dense(512)& 1 \\

@@

>>>>

		MobileNetV3Large-Layer[:270] + Soft-Attention + Metadata & 0.71 \\

@@

		MobileNetV3Large-Layer[:266] + Soft-Attention + Metadata  & 0.73 \\

@@

		MobileNetV3Large-Layer[:260] + Soft-Attention + Metadata  & 0.77 \\

@@

		MobileNetV3Large-Layer[:251] + Soft-Attention + Metadata  & 0.79 \\

@@

		MobileNetV3Large-Layer[:246] + Soft-Attention + Metadata  & 0.84 \\

@@

		MobileNetV3Large-Layer[:246] + Soft-Attention + Dense(512) + Metadata & 0.85 \\
		MobileNetV3Large-Layer[:240] + Soft-Attention + Metadata  & \textbf{0.86}\\
		MobileNetV3Large-Layer[:230] + Soft-Attention + Metadata  & 0.84 \\
		MobileNetV3Large-Layer[:230] + Soft-Attention + Metadata  & 0.81 \\
		MobileNetV3Large-Layer[:230] + Soft-Attention & 0.85 \\ 
		MobileNetV3Large & 0.85 \\ 

@@

\caption{Deeper analyzing of MobileNetV3Large Model}
\label{table:9}
In the MobileNetV3Large experiment, the model architecture is constructed by replacing the layers after the $28^th$ layer from the last layer by the Soft-Attention. The Table 9 demonstrate that, the Soft-Attention and the metadata have a good effect on the model. Otherwise, Adding a dense layer does not increase the model performance. The best MobileNetV3Large model architecture is the combination of MobileNetV3Large replaced from $241^th$ layer to the rest by Soft-Attention layer and the metadata, which peak the model performance of 0.86 accuracy rate. This is an optimized and balanced model, the parameters of model is indicated in Table 10.\\
	\begin{tabular}{| l | c |}
		Accuracy & 0.86\\
		Precision(avg) & 0.86\\
		F1-score(avg) & 0.86\\
		Sensitivity(avg) & 0.86\\
		Specificity(avg) & 0.95\\
		ROC AUC Score(avg) & 0.98\\
\caption{Performance of MobileNetV3Large}
\label{table:10}
